\graphicspath{{imgs/}}

%===============================================================================
\chapter{Introduction}
%===============================================================================



In \cite{Batchelor} we believe.


%-------------------------------------------------------------------------------

\section{Flow-assist droplet assembly}

material science,
photonic crystals,
microfluidics,
lab-on-a-chip.


\section{Liquid-infused surfaces}

drag reduction,
surface engineering,
superhydrophobicity,
lubricant-infused surfaces.


\section{Suspension flows}

particle suspensions,
complex fluids,
rheology,
shear thickening.

\thesisstructure Add here a brief description of the structure of the thesis.



%===============================================================================
\chapter{Microhydrodynamics}
%===============================================================================


This chapter summarizes the mathematical formulation and some basic theoretical ideas of microhydrodynamics and particle interactions.
By \emph{particle}, we loosely mean a solid or liquid body of micron to millimetre in size, which may also be referred to as \emph{droplet} for abuse of language.
As preliminaries, most of the contents are given without elaboration or proof. The interested reader is encouraged to read \cite{Batchelor, hb, ps, graham_2018} for greater details.

\bigskip

To begin with, recall the incompressible Navier-Stokes equation
\begin{subequations} \label{eq:Navier-Sotkes}
 \begin{equation}
   \nabla \cdot {\bm u} = 0,
  \label{eq:div-free}
 \end{equation}
 \begin{equation}
   \rho \bigg(\frac{\partial {\bm u}}{\partial t} + {\bm u} \cdot \nabla {\bm u} \bigg) = -\nabla p + \mu \nabla ^2  {\bm u} + {\bm f},
  \label{eq:NS}
 \end{equation}
\end{subequations}
relating the flow velocity $\bm u$ with the pressure $p$ in the presence of some force density $\bm f$, where $\rho$ and $\mu$ are the density and dynamic viscosity of the fluid, respectively.
Eq.\ \eqref{eq:Navier-Sotkes}, together with appropiate boundary conditions, governs the dynamics of a Newtonian fluid (which is what we consider throughout the thesis) that satisfies
\begin{equation}
 \begin{aligned}
   {\bm \sigma} = -p {\bm I}+ \mu \bigg( \nabla {\bm u} + (\nabla {\bm u})^T \bigg),
 \end{aligned}
\end{equation}
where $\bm \sigma$ is the stress tensor, and $\bm I$ the identity matrix.

Depending on the bounding material, conditions on the velocity or stress may be prescribed as the boundary condition. In the case of a solid boundary, it is usually the \emph{no-slip} velocity condition; while in the case of a liquid boundary, the following stress condition shall be satisfied,
\begin{equation} \label{eq:stress-bc}
  {\bm n} \cdot ({\bm \sigma}_+ - {\bm \sigma}_- )  = \gamma \kappa {\bm n} - \nabla \gamma,
\end{equation}
where $\bm n$ denotes the unit normal vector across the liquid interface (from $-$ to $+$), $\gamma$ the surface tension coefficent, and $\kappa$ the curvature of the interface (\eg $\kappa=2/a$ for a sphere of radius $a$). 

Eq.\ \eqref{eq:NS} can be further non-dimensionalized, using the reference length $L$, velocity $U$, time $T$, pressure $P \equiv \mu U/L$, and force density $F \equiv P/L$ scales, into
\begin{equation}
   \textrm{Re} \bigg(\textrm{Sr}^{-1} \frac{\partial \hat{\bm u}}{\partial \hat{t}} + \hat{\bm u} \cdot \hat{\nabla} \hat{\bm u} \bigg) =
   -\hat{\nabla} \hat{p} + \hat{\nabla} ^2  \hat{\bm u} + \hat{\bm f},
  \label{eq:NS-nondi}
\end{equation}
where the hat signifies dimensionless quantities, and Re and Sr represent the Reynolds and Strouhal numbers, defined as
\begin{equation}
  \begin{aligned}
    \textrm{Re} = \frac{\rho UL}{\mu},\quad \quad \textrm{Sr} = \frac{UT}{L}.
  \end{aligned}
\end{equation}
A capilary number can also be defined to non-dimensionalize the surface tension,
\begin{equation}
  \begin{aligned}
    \textrm{Ca} = \frac{\mu U}{\gamma}.
  \end{aligned}
\end{equation}



%-------------------------------------------------------------------------------

\section{Stokes flow and its symmetries}

When both Re and ReSr$^{-1}$ are small, Eq.\ \eqref{eq:NS-nondi} reduces to the Stokes equation,
\begin{equation}
   -\nabla p + \mu \nabla ^2  {\bm u} + {\bm f} = {\bm 0},
 \label{eq:Stokes}
\end{equation}
or, equivalently
\begin{equation}
   \nabla \cdot  {\bm \sigma} + {\bm f} = {\bm 0},
 \label{eq:Stokes1}
\end{equation}
which are written in the dimensional form.

Physically, the Stokes equation describes systems that are characterized by small length scales or are in slow motions typically encountered in microfluidic or biological applications.
For instance, the Reynolds number based on a 10 $\mu$m droplet traveling at a speed of 10 $\mu$m/s in water ($\rho=10^3$ kg/m$^{3}$, $\mu=10^{-3}$ Pa$\cdot$s) is $10^{-4}$;
and if there is no imposed frequency, the Strouhal number will be 1, thus both Re $\ll 1$ and ReSr$^{-1}$ $\ll 1$ are safely satisfied.

Mathematically, the removal of the nonlinear term in Eq.\ \eqref{eq:NS} can dramatically simplify the solution.
In general, the Stokes flow has the following symmetries and properties.

\begin{enumerate}
 \item \emph{Linearity}, which makes solutions to the Stokes equation superimposible. For example, if $({\bm u}_1,p_1)$ is a solution to ${\bm f}={\bm f}_1$ and $({\bm u}_2,p_2)$ is a solution to ${\bm f}={\bm f}_2$, then $(\alpha{\bm u}_1+\beta {\bm u}_2,\alpha p_1 + \beta p_2)$ is a solution to ${\bm f}=\alpha{\bm f}_1 + \beta {\bm f}_2$.
 \item \emph{Reversibility}, which follows from the linearity and entails that, if the forcing changes from ${\bm f}$ to $-{\bm f}$, then the flow should reverse, \ie $({\bm u},p) \to (-{\bm u},-p)$. While seemingly redundant, the reversibility symmetry can be very powerful in making \emph{reductio ad absurdum} type-of arguments, see \eg the classical note of \cite{Purcell1977}
 \item \emph{Stress equilibrium}, which states that any force exerted within the fluid is transmitted instantaneously to the boundary or, if there is no boundary, to infinity \citep{graham_2018}.
 \item \emph{Lorentz reciprocal identity}, which relates two solutions, $({\bm u}', {\bm \sigma}')$ and $({\bm u}'', {\bm \sigma}'')$ (they may differ by boundary conditions), of the Stokes equation by,
 \begin{equation}
  \small
  \begin{aligned}
   \int_V \bigg({\bm u}' \cdot (\nabla  \cdot {\bm \sigma}'') - {\bm u}'' \cdot (\nabla  \cdot {\bm \sigma}')\bigg) dV  & =\\
   \int_S \bigg({\bm u}' \cdot ({\bm n} \cdot {\bm \sigma}'') - {\bm u}'' \cdot ({\bm n} \cdot {\bm \sigma}')\bigg) dS, & 
  \end{aligned} \label{eq:lorentz-recip}
 \end{equation}
 where $V$ is some enclosed volume with surface $S$.
 \item \emph{Minimum dissipation principle}, which is a variational principle that asserts that the flow that minimizes the energy dissipation rate subject to incompressibility under certain boundary conditions is the Stokes flow under the same boundary conditions.
\end{enumerate}


\section{Single particle in Stokes flow}

Green's function (Stoekslet),
stresslet (symmetric and traceless),
scaling laws (decay),
Fax\'{e}n's law,
confinement,
multipole expansion,
boundary integral methods.


\section{Particle interactions}

Batchelor and Green (1972),
swapping,
dancing,
range of interactions,
dipolar theory,
lubrication approximation.


\section{Rheology}

microstructure,
many-body problems (theoretical difficulties),
macroscopic properties, averages and bulk stresses (see Brady and Bossis).

The behaviour of systems involving the motion of small particles relative to a suspending fluid covers a wide range of phenomena of interest to both scientists and engineers. Dense suspensions, where the volume fraction of solid particles becomes comparable to or even higher than that of the fluid (see Figure \ref{fig:snap}), have particularly rich and sometimes unexpected rheologies, such as yielding, shear thinning, continuous shear thickening (CST), or discontinuous shear thickening (DST) \citep{mewis_wagner_book, Morton_Morris_2014, guazzelli_pouliquen_2018, Morris_annurev2020}. Apart from being theoretically intriguing, these complex behaviours often have major implications in practice. For instance, while it makes sense for the cement industry to manufacture suspensions that do not shear thicken, the same feature becomes an advantage for designing flexible body armor.



%===============================================================================
\chapter{Numerical Methods}
%===============================================================================



limitation of theoretical approaches,
necessity of numerical solutions.

Despite the practical importance, theoretical development of suspension rheology remains chanllenging and only a few analytical solutions have been found in the dilute regime, see \eg \cite{Einstein_1906, batchelor_green_1972b}. This is partially due to a lack of precise knowledge or control of various interactions at the particle level, partially due to the mathematical difficulties involved in many-body problems. On the other hand, solving a system of interacting particles is relatively straightforward in an algorithmic perspective. In fact, the last decades have seen tremendous advancement in both numerical simulations and computer hardware.

governing equations.

numerical solutions.


%-------------------------------------------------------------------------------

\section{Fluid-resolved methods}

level set methods,
(interface-correction level set/ghost fluid method),
volume-of-fluid methods,
phase-field methods,
immersed boundary methods.


\section{Particle-based methods}

The central equation to solve is
\begin{equation} 
 \begin{aligned} \label{eq:force-balance}
  {\bm m} \cdot \frac{d{\bm U}}{dt} = {\bm F}^H + {\bm F}^P, 
 \end{aligned}
\end{equation}
where ${\bm m}$ is a generalized mass/moment-of-inertia matrix of dimension $6N \times 6N$,
${\bm U}$ is the particle translational/rotational velocity vector of dimension $6N$,
and ${\bm F}$ represent the $6N$ force/torque vectors owing to hydrodynamics (denoted with superscript $\footnotesize H$) or other interactions (denoted with superscript $\footnotesize P$). Specifically, ${\bm F}^P$ may include contact, electrostatic, van der Waars, or magnetic forces, \etc. In principle, stochastic forces can also be included in the general formulation, though its numerical treatments demand special care such that fluctuation-dissipation theorem is satified. In the present thesis, Brownian motions are neglected.

For inertialess particles in Stokes flow, the task is to solve Eq.\ \eqref{eq:force-balance} subject to ${\bm m} \cdot (d{\bm U}/dt) \to 0$. Various techniques exist as summarized below.

\subsection{Stokesian dynamics}

The Stokesian dynamics \citep{Brady_Bossis1988} employs the fact that, when the particle Reynolds number is small and the bulk flow is linear, the hydrodynamic forces and stresses exerted on the particles by the fluid can be expressed as
\begin{equation} 
 \begin{aligned} \label{eq:sd-hydro}
  \begin{pmatrix}
   {\bm F}^H \\
   {\bm S}^H
  \end{pmatrix}
  = - \mathscr{R} \cdot
  \begin{pmatrix}
   {\bm U}-{\bm U}^\infty \\
   -{\bm E}^\infty
  \end{pmatrix},
 \end{aligned}
\end{equation}
where
\begin{equation} 
 \begin{aligned}
  \mathscr{R} =
  \begin{pmatrix}
   {\bm R}_{FU} & {\bm R}_{FE} \\
   {\bm R}_{SU} & {\bm R}_{SE}
  \end{pmatrix},
 \end{aligned}
\end{equation}
is termed the ``grand resistance'' matrix. 
If $\mathscr{R}$ is known, 
formulate the problem as

It is calculated as
\begin{equation} 
 \begin{aligned}
  \mathscr{R} = (\mathscr{M}^\infty)^{-1} +\mathscr{R}_{2B} - \mathscr{R}_{2B}^\infty.
 \end{aligned}
\end{equation}          
Es.\ \eqref{eq:sd-hydro} is then inverted and integrated in time to obtain the dynamics.


\subsection{Dissipative particle dynamics}

dissipative particle dynamics (DPD) \citep{Hoogerbrugge_1992, Groot_Warren_1997}


\subsection{Discrete element methods}


discrete element methods (DEM) \citep{Mari_Seto_2014JoR, Cheal_Ness_2018}, to name a few.
 the discrete-element lubrication/contact dynamics (DLCD) model.




%===============================================================================
\chapter{Summary}
%===============================================================================






%%===============================================================================
%\chapter{Test chapter, a very very very long title to test the table of contents}
%%===============================================================================
%
%This chapter is meant for testing the correct referencing of figures, equations
%and tables.
%
%% equations
%%
%\begin{equation}
%	1 + 1 = 2
%	\label{eq:test_eq1}
%\end{equation}
%
%\begin{align}
%	2 + 2 = 4
%	\label{eq:test_eq2}
%\end{align}
%
%\begin{equation}
%	3 + 3 = 6
%	\label{eq:test_eq3_intro}
%\end{equation}
%
%% tables
%%
%\begin{table}
%	\centering
%	\begin{tabular}{c}
%		1
%	\end{tabular}
%	\caption{Test table 1}
%	\label{tab:test_tab1}
%\end{table}
%
%\begin{table}
%	\centering
%	\begin{tabular}{c}
%		2
%	\end{tabular}
%	\caption{Test table 2}
%	\label{tab:test_tab2}
%\end{table}
%
%\begin{table}
%	\centering
%	\begin{tabular}{c}
%		3
%	\end{tabular}
%	\caption{Test table 3}
%	\label{tab:test_tab3_intro}
%\end{table}
%
%% figures
%%
%\begin{figure}[h!]
%	\centering
%	test figure 1
%	\caption{Test figure 1}
%	\label{fig:test_fig1}
%\end{figure}
%
%\begin{figure}[h!]
%	\centering
%	test figure 2
%	\caption{Test figure 2}
%	\label{fig:test_fig2}
%\end{figure}
%
%\begin{figure}[h!]
%	\centering
%	test figure 3
%	\caption{Test figure 3}
%	\label{fig:test_fig3_intro}
%\end{figure}
%
%% test references
%%
%\hrule
%\begin{itemize}
%	\item reference to equation 1: \eqref{eq:test_eq1}
%	\item reference to equation 2: \eqref{eq:test_eq2}
%	\item reference to equation 3: \eqref{eq:test_eq3_intro}
%\end{itemize}
%\hrule
%\begin{itemize}
%	\item reference to table 1: \eqref{tab:test_tab1}
%	\item reference to table 2: \eqref{tab:test_tab2}
%	\item reference to table 3: \eqref{tab:test_tab3_intro}
%\end{itemize}
%\hrule
%\begin{itemize}
%	\item reference to figure 1: \eqref{fig:test_fig1}
%	\item reference to figure 2: \eqref{fig:test_fig2}
%	\item reference to figure 3: \eqref{fig:test_fig3_intro}
%\end{itemize}
%\hrule

%===============================================================================
% Acknowledgments
%===============================================================================
%
\input{acknowledgements}


%===============================================================================
% References
%===============================================================================
%
\bibliographystyle{jfm}
\bibliography{thesis}
%
\IfFileExists{overview.bbl}{\input{overview.bbl}}{}
